Interactive Visual Analysis of Image-Centric Cohort Study Data

### 2014-03-29 draft.tex
Added Figure Working files to repo, improved images

\subsubsection{Hypothesis-Based Analysis} \label{Hypothesis based Analysis}
\begin{figure}[htb]
 \centering
 %\includegraphics[width=1.5in]{figures/InteractionLoop}
 \includegraphics[width=3.5in]{figures/placeholder}
 \caption{\emph{Image is not final}. (a) "Did you experience back pain in the past three month" Yes No; (b) Clustering of Yes}
 \label{fig:hypopthesisbased}
\end{figure}
%
If the user has already a hypothesis about a relation between a non-image feature regarding shape the workflow slightly differs from the hypothesis-free analysis.
%
The starting point of the analysis is a \emph{feature investigation}, where a feature of interest is selected by dragging it into the canvas area and view the subjects distribution as well as their shape differences.
%
In our use case, the epidemiologist was interested in the dichotomous questionnaire answer to "Did you experience back pain in the past three month".
%
The mean shapes of the resulting visualization as seen in Figure~\ref{fig:hypopthesisbased} (a) show no difference between the two groups.
%
Either there are no differences or the variance information was lost in the mean-shape calculation.
%
Since the focus is on subjects which suffer from back pain, the clustering result of these subjects are then drawn into the canvas area, yielding six cluster as seen in Figure~\ref{fig:hypopthesisbased} (b).
%
Cluster 5 stood out for having a so-called hyperlordosis, a strong curvature of the lumbar spine which is a indicator for back pain.

>>>>

\subsubsection{Hypothesis-Based Analysis} \label{Hypothesis based Analysis}
\begin{figure}[htb]
 \centering
 %\includegraphics[width=1.5in]{figures/InteractionLoop}
 \includegraphics[width=3.5in]{figures/hypothesisbased}
 \caption{(a) Dichotomous questionnaire answer to "Did you experience back pain in the past three month".
 %
 Mean-Shapes between the groups show no difference.
 %
 (b) Shape-based clustering for all subjects who suffered from back-pain yields 6 groups. 
 %
 Note that the difference in subject count is due to the missing shape information for some subjects.
 %
% The total count of subjects in (b) is smaller 
 }
 \label{fig:hypopthesisbased}
\end{figure}
%
If the user has already a hypothesis about a relation between a non-image feature regarding shape the workflow slightly differs from the hypothesis-free analysis.
%
The starting point of the analysis is a \emph{feature investigation}, where a feature of interest is selected by dragging it into the canvas area and view the subjects distribution as well as their shape differences.
%
In our use case, the epidemiologist was interested in the dichotomous questionnaire answer to "Did you experience back pain in the past three month".
%
The mean shapes of the resulting visualization as seen in Figure~\ref{fig:hypopthesisbased} (a) show no difference between the two groups.
%
Either there are no differences or the variance information was lost in the mean-shape calculation.
%
Since the focus is on subjects which suffer from back pain, the clustering result of these subjects are then drawn into the canvas area, yielding six cluster as seen in Figure~\ref{fig:hypopthesisbased} (b).
%
Cluster 5 stood out for having a so-called hyperlordosis, a strong curvature of the lumbar spine which is a indicator for back pain.
